---
title: "Homework 6"
author: "Jialu Cheng (jc5457)"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

### Problem 2

**Data Loading**

Loading the data that the Washington Post gathered on homicides in 50 large U.S. cities.
```{r}
homicides = read_csv(file= "./data/homicide-data.csv") %>%
janitor::clean_names()
```


**Data Cleaning**

Create a `city_state` variable (e.g. “Baltimore, MD”), and a binary variable `solved` indicating whether the homicide is solved. 

Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. 

For this problem, limit your analysis those for whom `victim_race` is `white` or `black`. Be sure that `victim_age` is numeric.

```{r}
homicides_clean = 
  homicides %>%
  mutate(
    state = replace(state, state== "wI", "WI"),
    city_state= paste(city, state, sep= ","),
    solved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age)
    ) %>% 
  filter(
    !city_state %in% c("Dallas,TX","Phoenix,AZ", "Kansas City,MO","Tulsa,AL"), 
    victim_race %in% c("White","Black")
    )
```

**Fitting GLM for Baltimore, MD**

For the city of Baltimore, MD, use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. 

Save the output of `glm` as an R object; apply the `broom::tidy` to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
Baltimore_GLM = 
  homicides_clean %>% 
  filter(city_state == "Baltimore,MD") %>% 
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

Baltimore_GLM %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>% 
  select(term, OR, p.value) %>% 
  knitr::kable(digits = 2) 

CI = 
  exp(confint(Baltimore_GLM, level= 0.95))
```


The adjusted odds ratio is 0.43 for solving homicides comparing male victims to female victims keeping all other variables fixed, and the confidence interval is (0.32, 0.56). 

On average, the odds of resolving homicides in which the victim is Male are 0.43 times of that in which the victim is female, keeping all other variables fixed.


**Fitting GLM for all cities**

Now run `glm` for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. 
Do this within a “tidy” pipeline, making use of `purrr::map`, list columns, and `unnest` as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
all_GLM = 
  homicides_clean %>% 
  nest(data = -city_state) %>% 
  mutate(
    model_output = map(data, 
                       ~glm(solved ~ victim_age + victim_race + victim_sex, data = ., 
                            family = binomial())),
    results = purrr::map(model_output, broom::tidy, conf.int = TRUE)
  ) %>% 
  select(city_state, results) %>% 
  unnest(cols = results) %>% 
  filter(term== "victim_sexMale") %>% 
  mutate(OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  select(city_state, term, OR, conf.low, conf.high)
```


**Plotting**

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
ggplot(
  all_GLM %>% 
    mutate(city_state= fct_reorder(city_state, OR)), 
  aes(x= city_state, y= OR, color=city_state)
  )+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low, ymax= conf.high))+
  theme_classic()+ 
  theme(legend.position= "none")+
  theme(plot.title = element_text(hjust= 0.5, size=12),
        axis.text.x.bottom = element_text(size= 8, angle= 90))+
    labs(x = "City",
         y= "Odds Ratio",
         title = "OR and 95%CIs of Resolved Homicide Cases in Large US Cities, Comparing Males to Females")
```

The plot shows estimated OR with 95% confidence interval of resolved homicides, comparing male victims and female victims, for the 50 largest cities in the US, in the order of lowest to highest OR.

* `New York, NY` has the lowest OR with a relatively narrow 95% CI for resolved cases of male victims compared to female victims. 

* `Albuquerque,NM` has the highest OR with a relatively wide 95% CI for resolved cases of male victims compared to female victims. 



### Problem 3

